\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-03-11 doc/manuscript.tex
trivia

\begin{table}[htp]
	\caption{\label{tab:eco-evo-pars}Parameters and parameter values for the eco-evolutionary case study. Values are assigned at
		at the start of \texttt{genetic\_diversity\_master.R}. ``Name" refers to the variable declared in the computer code. Where appropriate, the corresponding symbols from equations in Appendix \ref{eco-evo} are shown in parentheses. }
	\centering
	\smallskip 
	\begin{tabular}{lrl}
		\hline
		Name & Values & Definition \\
		\hline
		Tstdev & 1 & Standard deviation of temperature (interannual variation) \\
		baseT & -1 & Baseline temperature \\
		deltaT & 5 & Total change in temperature \\
		baseline\_yrs & 500 & Number of years at baseline temperature used to fit statistical models \\
		warming\_yrs & 100  & Number of years over which temperature increases \\
		final\_yrs & 300  & Number of years at steady-state, elevated temperature \\
		\hline
		fec\_Tmu & -1,0,1  & Optimal temperature for genotypes AA, Aa, and aa, respectively \\
		fec\_Tsigma & 8  & Standard deviation in fecundity for all genotypes \\
		fec\_max & 100 &  Maximum fecundity for all genotypes \\
		G ($g$) & 1 & Germination rate for all genotypes \\
		seedSurv ($s$)  &  0.5  & Survival rate for ungerminated seeds of all genotypes \\
		alpha ($\alpha$) & 1  &  All competition coefficients for all genotypes \\
		\hline

>>>>

\begin{table}[htp]
	\caption{\label{tab:eco-evo-pars}Parameters and parameter values for the eco-evolutionary case study. Values are assigned at
		at the start of \texttt{genetic\_diversity\_master.R}. ``Name" refers to the variable declared in the computer code. Where appropriate, the corresponding symbols from equations in Appendix \ref{eco-evo} are shown in parentheses. }
	\centering
	\smallskip 
	\begin{tabular}{lrl}
		\hline
		Name & Values & Definition \\
		\hline
		Tstdev & 1 & Standard deviation of temperature (interannual variation) \\
		baseT & -1 & Baseline temperature \\
		deltaT & 5 & Total change in temperature \\
		baseline\_yrs & 500 & Number of years at baseline temperature used to fit statistical models \\
		warming\_yrs & 100  & Number of years over which temperature increases \\
		final\_yrs & 300  & Number of years at steady-state, elevated temperature \\
		\hline
		fec\_Tmu & -1,0,1  & Optimal fecundity temperature for genotypes AA, Aa, and aa \\
		fec\_Tsigma & 8  & Standard deviation in fecundity for all genotypes \\
		fec\_max & 100 &  Maximum fecundity for all genotypes \\
		G ($g$) & 1 & Germination rate for all genotypes \\
		seedSurv ($s$)  &  0.5  & Survival rate for ungerminated seeds of all genotypes \\
		alpha ($\alpha$) & 1  &  All competition coefficients for all genotypes \\
		\hline
